On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-26 docs/mvfits_paper/mvf.tex
misc updates

Only where $\jf \cw\lmn=0$ does $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.

@@

The consequences of that choice, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.

@@

For the so-called \textit{Phenom} models, the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.

>>>>

Only where $\jf \cw\lmn=0$ do $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.

@@

The consequences of that approximation, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,Berti:2014fga,London:2018gaq}.

@@

This approximation also applies to many of the so-called \textit{Phenom} models, where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
